Flatiron cleaning

### 2022-05-20 Rmd/Manuscript rdi analysis.Rmd
Add stratified analysis for histology

```{r library, include=FALSE}
library(tidyverse)
library(data.table)
library(lubridate)
library(irr)
library(ggplot2)
library(gtsummary)
library(survminer)
library(survival)
library(mice)
```

@@

Are excluded :  
-	Data from one PracticeID  (Flatiron requested removal of this practice ID from the dataset)  
-	Certain historical structured data were not available for patients seen at academic sites prior to 2015 – Flatiron has asked that if conducting survival analyses, these patients are removed (patients diagnosed < 2015 at academic sites)  
```{r}
flatiron_rec <- RDI_data_per_patients %>% 
  filter(is.na(flatiron_rules))
```

@@

-	exclude borderline cases (not invasive ovarian cancer)  
- exclude patients whose histology is unknown  
- remove chemotherapy only patients  
- include only patients who received platin and/or taxane (exclude patients who didn't received carboplatin)  
- exclude patients who only received neo + surgery  
- include patients with single or dual P/T +/- Bev as frontline treatment
```{r}
study_criteria <- flatiron_rec %>% 
  filter(is.na(borderline))

@@

```{r}
missing_data <- study_criteria %>% 
  filter(!(issurgery == "Yes" & is.na(surgerydate)))

@@

- exclude patients with more than 1 line as Neo
- exclude patients with maintenance within their frontline
- exclude patients with more than 6 cycles in Neo, more than 9 cycles **total** in upfront chemo or more than 9 cycles in upfront surgery
- Exclude patients that received wrong dose dense of 1 carbo + 2 paclitaxel
- exclude patients who switch drug within a line
```{r}
standard_care <- missing_data %>% 
  # Remove patients with more than 1 line as Neo
  filter(is.na(neo_more_more_than_1line))

@@

### For Upfront Chemo
```{r}
data <- Frontline %>% 
  filter(therapy == "Upfront Chemo") %>% 
  select(patientid, month_at_os_from_treatment, vital_status, 
         raceeth, diagnosisdate, surgerydate,
         ageatdx, stagecat, debulking, histology,
         RDI_carbo_neo, RDI_pacli_neo, 
         RDI_carbo_adj, RDI_pacli_adj
         # therapy
  )
nonimp_cox_model <-
  coxph(Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology,
        data = data)
# nonimp_cox_model

@@

<!-- Imputation and cox regression model on imputed data using the new predictor matrix. -->
```{r}
# Start imputations using mice
Cox.imp <- mice(dataset, m=5, maxit=50, 
                predictorMatrix=Pred,
                seed=123, printFlag=F)
check1 <- with(data = Cox.imp,
       exp = coxph(
         Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology
       ))
# pool(check1)$pooled
multiple_imputations_number <- round(max(pool(check1)$pooled$fmi),2)*100
```

@@

fit.Cox <-
  with(data = Cox.imp,
       exp = coxph(
         Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology
       ))

@@

```{r}
data <- Frontline %>% 
  filter(therapy == "Upfront Surgery") %>% 
  select(patientid, month_at_os_from_treatment, vital_status, 
         raceeth, diagnosisdate, surgerydate,
         ageatdx, stagecat, debulking, histology,
         RDI_carbo_adj, RDI_pacli_adj
         # therapy
  )
nonimp_cox_model <-
  coxph(Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology,
        data = data)
# nonimp_cox_model

@@

<!-- Imputation and cox regression model on imputed data using the new predictor matrix. -->
```{r}
# Start imputations using mice
Cox.imp <- mice(dataset, m=5, maxit=50, 
                predictorMatrix=Pred,
                seed=123, printFlag=F)
check1 <- with(data = Cox.imp,
       exp = coxph(
         Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology
       ))
# pool(check1)$pooled
multiple_imputations_number <- round(max(pool(check1)$pooled$fmi),2)*100
```

@@

fit.Cox <-
  with(data = Cox.imp,
       exp = coxph(
         Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology
       ))

@@

<!-- Complete the data and merge with original -->
```{r}
imputed_data_surg <- complete(Cox.imp, include = FALSE) %>% 
  rename(imp_stagecat = stagecat, imp_debulking = debulking)

@@

    missing_data = study_criteria  %>% 
    filter(!(issurgery == "Yes" & is.na(surgerydate))) %>%
    filter(is.na(gap_surg_drugs)) %>%
    filter(days_at_first_drug >= 0 &
             (is.na(surgerydate) | days_at_surg >= 0)) %>%
    filter((
      therapy == "Upfront Chemo" &
        (!is.na(RDI_carbo_neo) & !is.na(RDI_pacli_neo) & 
           !is.na(RDI_carbo_adj) & !is.na(RDI_pacli_adj)) 
    ) | (
      therapy == "Upfront Surgery" &
        (!is.na(RDI_carbo_adj) & !is.na(RDI_pacli_adj))
    )
    ),

    standard_care = missing_data %>% 
    filter(is.na(neo_more_more_than_1line)) %>%
    filter(is.na(frontline_has_maintenance)) %>%
    filter(is.na(too_many_cycle)) %>% 
    filter(is.na(wrong_pacli_dosedense)) %>%
    filter(is.na(switch_drugs)),

@@

study_consort <- study_cohorts %>%
  consort_box_add(
    "full", 0, 40, cohort_count_adorn(study_cohorts, .full)
  ) %>%
  consort_box_add(
    "exc_flatiron_rec", 0.2, 35, glue::glue(
      "{cohort_count_adorn(study_cohorts, excluded1)}<br> 
      • <span style='color:darkgreen'>**90 days rule between diagnosis and treatment**</span> <br>
      • 30 days rule excluding patient who didn't survive <br> for at least 30 days after diagnosis <br>
      • **(Data from one PracticeID)** <br>
      • **(historical structured data were not available for <br> patients seen at academic sites prior to 2015)**
      ")
  ) %>%
  consort_box_add(
    "flatiron_rec", 0, 30, cohort_count_adorn(study_cohorts, flatiron_rec)
  ) %>%
  consort_box_add(
    "exc_study_criteria", 0.2, 25, glue::glue(
      "{cohort_count_adorn(study_cohorts, excluded2)}<br> 
      • Borderline cases (not invasive ovarian cancer) <br>
      • exclude patients whose histology is unknown <br>
      • remove chemotherapy only patients <br>
      • include patients who received carboplatin +/- taxane +/- Bev in a adj +/- neo settings
      ")
  ) %>%
  consort_box_add(
    "study_criteria", 0, 20, cohort_count_adorn(study_cohorts, study_criteria)
  ) %>%
  consort_box_add(
    "exc_missing_data", 0.2, 15, glue::glue(
      "{cohort_count_adorn(study_cohorts, excluded3)}<br> 
      • exclude the patients who had surgery but we don’t have a date of surgery -> NONE removed anymore <br> 
      • remove patients with long gap between surgery and adjuvant start (3 months) -> NONE removed anymore <br> 
      • exclude patients with a date of drug or date of surgery BEFORE diagnosis will be excluded (inclined to be wrongly recorded) <br> 
      • exclude patients for whose no RDI were available
      ")
  ) %>%
  consort_box_add(
    "missing_data", 0, 10, cohort_count_adorn(study_cohorts, missing_data)
  ) %>%
  consort_box_add(
    "exc_standard_care", 0.2, 5, glue::glue(
      "{cohort_count_adorn(study_cohorts, excluded4)}<br> 
      • exclude patients with more than 1 line as Neo <br> 
      • exclude patients with maintenance within their frontline <br> 
      • exclude patients with more than 6 cycles in Neo, more than 9 cycles total in upfront chemo or more than 9 cycles in upfront surgery
      ")
  ) %>%
  consort_box_add(
    "Frontline", 0, 0, cohort_count_adorn(study_cohorts, Frontline)
  ) %>%

@@

Used the ICC for a single rater, two-way mixed effects model with a measure for absolute agreement (two-way mixed-effects model and the absolute agreement are recommended for both test-retest and intra-rater reliability studies (Koo et al., 2016).  
<!-- **For ICC, a value of 0.9 is considered as excellent.**  -->
```{r}
# Need to recalculate the average per cycle as we did it by line (was comaing back to same because we limit our study to 1+1 or 1+3 cycle type)
# What I did :
# Treatment <- Treatment %>% 
#   mutate(relative_dose_intensity = amount / expected_dose # adjusted_expected_dose
#   ) %>%
#   group_by(patientid, chemotherapy_type, drugname) %>%
#   mutate(mean_RDI_per_drug = round(mean(relative_dose_intensity, na.rm = TRUE), 3)
#   ) %>% 
#   ungroup()

@@

```{r}
ICC_df <- Treatment_ICC %>% select(patientid, chemotherapy_type, cycle_increment, mean_RDI_per_cycledrug) %>% 
  unite(patientid, c(patientid:chemotherapy_type)) %>%
      pivot_wider(names_from = cycle_increment, values_from = mean_RDI_per_cycledrug) %>%
      select(-patientid)

icc_value <- round(icc(
      ICC_df, model = "twoway", 
      type = "agreement", unit = "single"
    )$value, 3)
head(ICC_df, 10)

# mutate(reliability = case_when(
#   value < 0.5 ~ "poor",
#   value >= 0.5 &
#     value < 0.75 ~ "moderate",
#   value >= 0.75 &
#     value < 0.9 ~ "good",
#   value >= 0.9 ~ "excellent"
# ))
```
The ICC value is equal to `r icc_value` which means that `r paste("the reliability is", ifelse(icc_value < 0.5, "poor", ifelse( icc_value <0.75, "moderate",ifelse(icc_value<0.9, "good", "excelent"))))`

```{r}
full_data_study_pop <-
  Treatment %>%
  filter(str_detect(patientid, paste(Frontline$patientid, collapse = "|"))) %>%
  arrange(patientid, episodedate, drugname) %>% 
  filter(had_carbo == "Yes") %>% 
  filter(linenumber_adj == 1)
```

@@

## <span style="color:green">**Table S0 Summary of the expected, actual dose, and RDI, Crcl, ...**</span>
Here we calculated the mean of amount, CrCl, BSA, height, weight, creatinine,
         target_auc, expected_dose, dose received, 
         RDI per patient/therapy/settings for each drug name.  
The tables show the median IQR for carboplatin calculated over patients with the same therapy (Upfront C or S) and setting (Neo or Adj).
```{r Summary of the expected, actual dose, and RDI}
tbl <- 
  Treatment %>% 
  # Limit to the patietns after exclusion criteria
  filter(str_detect(patientid, paste(Frontline$patientid, collapse = "|"))) %>% 
  arrange(patientid, episodedate, drugname) %>% 
  # group to have RDI by cycle for each drug 
  # group_by(patientid, chemotherapy_type, cycle_increment, drugname) %>%
  # mutate(mean_RDI_per_cycledrug = round(mean(relative_dose_intensity, na.rm = TRUE), 3)
  # ) %>% 
  # ungroup() %>% 
  filter(drugname == "carboplatin") %>% 
  filter(linenumber_adj == 1) %>%

  group_by(patientid, therapy, chemotherapy_type, drugname) %>% 
  summarise(amount = mean(amount), 
            BSA = mean(BSA), 
            height = mean(height), 
            weight = mean(weight), 
            creatinine = mean(creatinine),
            CrCl = mean(CrCl),
            target_auc = mean(target_auc),
            expected_dose = mean(expected_dose),
            relative_dose_intensity = mean(mean_RDI_per_drug)) %>% 
  ungroup() %>% 
  mutate(chemotherapy_type = factor(chemotherapy_type, levels = c("Neoadjuvant", "Adjuvant")))

@@

<!-- ## 2.Treatment Plots -->
<div class = "row">
<div class = "col-md-6">
```{r treatment plots}
full_data_study_pop %>% 
  filter(chemotherapy_type == "Neoadjuvant") %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linename) %>% 
  tbl_summary(label = list(linename ~ "line name received as Neoadujant"))
full_data_study_pop %>% 
  filter(chemotherapy_type == "Adjuvant" & linenumber_adj == 1) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linename, therapy) %>% 
  tbl_summary(by = therapy,
              label = list(linename ~ "line name received as Adjuvant"))
```
</div>

<div class = "col-md-6">
```{r}
full_data_study_pop %>% 
  filter(chemotherapy_type == "Neoadjuvant") %>% 
  group_by(patientid, drugname) %>% 
  summarise(CrCl = mean(CrCl),
            target_auc = mean(target_auc),
            expected_dose = mean(expected_dose)) %>% 
  ungroup() %>% 
  distinct(patientid, drugname, .keep_all = TRUE) %>% 
  select(CrCl, target_auc, expected_dose, drugname) %>% 
  tbl_summary(by = drugname,
              label = list(CrCl ~ "Average CrCl during Neoadujant setting",
                           target_auc ~ "Target dose (AUC or mg/mg2)",
                           expected_dose ~ "Expected dose")
    )
```
</div>
</div>

@@

## 1.Plots RDI
## <span style="color:green">**Figure 1: Ridge**</span>  
You said to limint the x axis at 2 but we will lose the little bump....Do you want 2?  
Do you want the blue and red lines?
```{r ggridges, fig.width=16, fig.height=18}
library(ggridges)
# Frontline %>% 
#   pivot_longer(cols = c(RDI_carbo_neo, RDI_pacli_neo, RDI_carbo_adj, RDI_pacli_adj)) %>% 
#   filter(!is.na(value)) %>% 
#   ggplot(aes(y=raceeth, x=value,  fill=raceeth
#              )) +
#     geom_density_ridges(alpha=0.5) +
#     theme_ridges()+
#   theme(#text = element_text(size = 14),#axis.text.y = element_blank(),
#         panel.spacing = unit(0.1, "lines"),
#         strip.text.x = element_text(size = 14)
#     ) +
#   geom_vline(xintercept = 1, color = "red", linetype = 2)+
#   geom_vline(xintercept = 0.85, color = "blue", linetype = 2)+
# 
#   facet_wrap(therapy ~ name, ncol = 2, scales = "free_x")

@@

## <span style="color:green">**Table 2: Summary RDI data by race and bmi**</span>  
Platin  
```{r Table 7 Summary RDI data by race and bmi}
tbl1 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
  select(c(raceeth, "RDI" = RDI_carbo_neo, "RDI cat" = RDI_carbo_neo_grp)) %>%
  tbl_summary(by = raceeth) %>%
  bold_labels() %>% 
  add_p() %>% bold_p(t= 0.05)
tbl2 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
  select(c(bmi_cat, "RDI" = RDI_carbo_neo, "RDI cat" = RDI_carbo_neo_grp)) %>%
  tbl_summary(by = bmi_cat) %>%
  bold_labels() %>% 
  add_p() %>% bold_p(t= 0.05)

tbl3 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
  select(c(raceeth, "RDI" = RDI_carbo_adj, "RDI cat" = RDI_carbo_adj_grp)) %>%
  tbl_summary(by = raceeth) %>%
  bold_labels() %>% 
  add_p() %>% bold_p(t= 0.05)
tbl4 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
  select(c(bmi_cat, "RDI" = RDI_carbo_adj, "RDI cat" = RDI_carbo_adj_grp)) %>%
  tbl_summary(by = bmi_cat) %>%
  bold_labels() %>% 
  add_p() %>% bold_p(t= 0.05)

@@

tbl5 <- Frontline %>% filter(therapy == "Upfront Surgery") %>%
  select(c(raceeth, "RDI" = RDI_carbo_adj, "RDI cat" = RDI_carbo_adj_grp)) %>%
  tbl_summary(by = raceeth) %>%
  bold_labels() %>% 
  add_p() %>% bold_p(t= 0.05)
tbl6 <- Frontline %>% filter(therapy == "Upfront Surgery") %>%
  select(c(bmi_cat, "RDI" = RDI_carbo_adj, "RDI cat" = RDI_carbo_adj_grp)) %>%
  tbl_summary(by = bmi_cat) %>%
  bold_labels() %>% 
  add_p() %>% bold_p(t= 0.05)

>>>>

```{r library, include=FALSE}
library(tidyverse)
library(data.table)
library(lubridate)
library(psych)
library(ggplot2)
library(gtsummary)
library(survminer)
library(survival)
library(mice)
```

@@

Are excluded :  
-	Data from one PracticeID  (Flatiron requested removal of this practice ID from the dataset)  
-	Certain historical structured data were not available for patients seen at academic sites prior to 2015 – Flatiron has asked that if conducting survival analyses, these patients are removed (patients diagnosed < 2015 at academic sites)  
```{r flatiron_rec}
flatiron_rec <- RDI_data_per_patients %>% 
  filter(is.na(flatiron_rules))
```

@@

-	exclude borderline cases (not invasive ovarian cancer)  
- exclude patients whose histology is unknown  
- remove chemotherapy only patients  
- include only patients who received platin and/or taxane (exclude patients who didn't received carboplatin)  
- exclude patients who only received neo + surgery  
- include patients with single or dual P/T +/- Bev as frontline treatment
```{r study_criteria}
study_criteria <- flatiron_rec %>% 
  filter(is.na(borderline))

@@

```{r missing_data}
missing_data <- study_criteria %>% 
  filter(!(issurgery == "Yes" & is.na(surgerydate)))

@@

- exclude patients with other than intravenous drugs
- exclude patients with more than 1 line as Neo
- exclude patients with maintenance within their frontline
- exclude patients with more than 6 cycles in Neo, more than 9 cycles **total** in upfront chemo or more than 9 cycles in upfront surgery
- Exclude patients that received wrong dose dense of 1 carbo + 2 paclitaxel
- exclude patients who switch drug within a line
```{r standard_care}
standard_care <- missing_data %>% 
  # Remove patients with more than 1 line as Neo
  filter(is.na(neo_more_more_than_1line)) %>% 
  filter(is.na(intravenous_rule))

@@

### For Upfront Chemo
```{r imputation up Chemo}
data <- Frontline %>% 
  filter(therapy == "Upfront Chemo") %>% 
  select(patientid, month_at_os_from_treatment, vital_status, 
         raceeth, diagnosisdate, surgerydate,
         ageatdx, stagecat, debulking, histology,
         RDI_carbo_neo, RDI_pacli_neo, 
         RDI_carbo_adj, RDI_pacli_adj
         # therapy
  )
nonimp_cox_model <-
  coxph(Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_neo + RDI_carbo_adj + raceeth + ageatdx + stagecat + debulking + histology,
        data = data)
# nonimp_cox_model

@@

<!-- Imputation and cox regression model on imputed data using the new predictor matrix. -->
```{r}
# Start imputations using mice
Cox.imp <- mice(dataset, m=5, maxit=50, 
                predictorMatrix=Pred,
                seed=123, printFlag=F)
check1 <- with(data = Cox.imp,
       exp = coxph(
         Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_neo + RDI_carbo_adj + raceeth + ageatdx + stagecat + debulking + histology
       ))
# pool(check1)$pooled
multiple_imputations_number <- round(max(pool(check1)$pooled$fmi),2)*100
```

@@

fit.Cox <-
  with(data = Cox.imp,
       exp = coxph(
         Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_neo + RDI_carbo_adj + raceeth + ageatdx + stagecat + debulking + histology
       ))

@@

```{r imputation up Surgery}
data <- Frontline %>% 
  filter(therapy == "Upfront Surgery") %>% 
  select(patientid, month_at_os_from_treatment, vital_status, 
         raceeth, diagnosisdate, surgerydate,
         ageatdx, stagecat, debulking, histology,
         RDI_carbo_adj, RDI_pacli_adj
         # therapy
  )
nonimp_cox_model <-
  coxph(Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + stagecat + debulking + histology,
        data = data)
# nonimp_cox_model

@@

<!-- Imputation and cox regression model on imputed data using the new predictor matrix. -->
```{r}
# Start imputations using mice
Cox.imp <- mice(dataset, m=5, maxit=50, 
                predictorMatrix=Pred,
                seed=123, printFlag=F)
check1 <- with(data = Cox.imp,
       exp = coxph(
         Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + stagecat + debulking + histology
       ))
# pool(check1)$pooled
multiple_imputations_number <- round(max(pool(check1)$pooled$fmi),2)*100
```

@@

fit.Cox <-
  with(data = Cox.imp,
       exp = coxph(
         Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + stagecat + debulking + histology
       ))

@@

<!-- Complete the data and merge with original -->
```{r combine imputed data}
imputed_data_surg <- complete(Cox.imp, include = FALSE) %>% 
  rename(imp_stagecat = stagecat, imp_debulking = debulking)

@@

    missing_data = study_criteria  %>% 
    filter(!(issurgery == "Yes" & is.na(surgerydate))) %>%
    filter(is.na(gap_surg_drugs)) %>%
    filter(days_at_first_drug >= 0 &
             (is.na(surgerydate) | days_at_surg >= 0)) %>%
    filter((
      therapy == "Upfront Chemo" &
        (!is.na(RDI_carbo_neo) & 
           !is.na(RDI_carbo_adj)) 
    ) | (
      therapy == "Upfront Surgery" &
        (!is.na(RDI_carbo_adj))
    )
    ),

    standard_care = missing_data %>% 
    filter(is.na(neo_more_more_than_1line)) %>%
    filter(is.na(intravenous_rule)) %>% 
    filter(is.na(frontline_has_maintenance)) %>%
    filter(is.na(too_many_cycle)) %>% 
    filter(is.na(wrong_pacli_dosedense)) %>%
    filter(is.na(switch_drugs)),

@@

study_consort <- study_cohorts %>%
  consort_box_add(
    "full", 0, 40, cohort_count_adorn(study_cohorts, .full)
  ) %>%
  consort_box_add(
    "exc_flatiron_rec", 0.2, 35, glue::glue(
      "{cohort_count_adorn(study_cohorts, excluded1)}<br> 
      • <span style='color:darkgreen'>**90 days rule between diagnosis and treatment**</span> <br>
      • 30 days rule excluding patient who didn't survive <br> for at least 30 days after diagnosis
      ")
  ) %>%
  consort_box_add(
    "flatiron_rec", 0, 30, cohort_count_adorn(study_cohorts, flatiron_rec)
  ) %>%
  consort_box_add(
    "exc_study_criteria", 0.2, 25, glue::glue(
      "{cohort_count_adorn(study_cohorts, excluded2)}<br> 
      • Borderline cases (not invasive ovarian cancer) <br>
      • exclude patients whose histology is unknown <br>
      • remove chemotherapy only patients <br>
      • include patients who received carboplatin +/- taxane +/- Bev in a adj +/- neo settings
      ")
  ) %>%
  consort_box_add(
    "study_criteria", 0, 20, cohort_count_adorn(study_cohorts, study_criteria)
  ) %>%
  consort_box_add(
    "exc_missing_data", 0.2, 15, glue::glue(
      "{cohort_count_adorn(study_cohorts, excluded3)}<br> 
      • exclude the patients who had surgery but we don’t have a date of surgery -> NONE removed anymore <br> 
      • remove patients with long gap between surgery and adjuvant start (3 months) -> NONE removed anymore <br> 
      • exclude patients with a date of drug or date of surgery BEFORE diagnosis will be excluded (inclined to be wrongly recorded) <br> 
      • exclude patients for whose no RDI were available
      ")
  ) %>%
  consort_box_add(
    "missing_data", 0, 10, cohort_count_adorn(study_cohorts, missing_data)
  ) %>%
  consort_box_add(
    "exc_standard_care", 0.2, 5, glue::glue(
      "{cohort_count_adorn(study_cohorts, excluded4)}<br> 
      • exclude patients with more than 1 line as Neo <br> 
      • exclude patients with maintenance within their frontline <br> 
      • exclude patients with more than 6 cycles in Neo, more than 9 cycles total in upfront chemo or more than 9 cycles in upfront surgery
      ")
  ) %>%
  consort_box_add(
    "Frontline", 0, 0, cohort_count_adorn(study_cohorts, Frontline)
  ) %>%

@@

Used the ICC for a average raters, two-way mixed effects model with a measure for absolute agreement (two-way mixed-effects model and the absolute agreement are recommended for intra-rater reliability studies (Koo et al., 2016).  
<!-- **For ICC, a value of 0.9 is considered as excellent.**  -->
```{r ICC data prep}
# Need to recalculate the average per cycle as we did it by line (it was more simple and was coming back to same because we limit our study to 1+1 or 1+3 cycle type)
# What I did :
# Treatment <- Treatment %>% 
#   mutate(relative_dose_intensity = amount / expected_dose # adjusted_expected_dose
#   ) %>%
#   group_by(patientid, chemotherapy_type, drugname) %>%
#   mutate(mean_RDI_per_drug = round(mean(relative_dose_intensity, na.rm = TRUE), 3)
#   ) %>% 
#   ungroup()

@@

### Upfront Chemo Neo
```{r ICC}
ICC_df <- Treatment_ICC %>% 
  filter(therapy == "Upfront Chemo" & chemotherapy_type == "Neoadjuvant") %>% 
  select(patientid, cycle_increment, mean_RDI_per_cycledrug) %>% 
      pivot_wider(names_from = cycle_increment, values_from = mean_RDI_per_cycledrug) %>%
      select(-patientid)

icc_value <- ICC(ICC_df)$results[4, 2]
lb_value <- ICC(ICC_df)$results[4, 7]
up_value <- ICC(ICC_df)$results[4, 8]
# mutate(reliability = case_when(
#   value < 0.5 ~ "poor",
#   value >= 0.5 &
#     value < 0.75 ~ "moderate",
#   value >= 0.75 &
#     value < 0.9 ~ "good",
#   value >= 0.9 ~ "excellent"
# ))
```
The ICC value in Upfront Chemo Neo setting is equal to `r icc_value` which means that `r paste("the reliability is", ifelse(icc_value < 0.5, "poor", ifelse( icc_value <0.75, "moderate",ifelse(icc_value<0.9, "good", "excelent"))))`.  
Lower bound and higher bound are `r lb_value` - `r up_value` respectively.

### Upfront Chemo Adj
```{r}
ICC_df <- Treatment_ICC %>% 
  filter(therapy == "Upfront Chemo" & chemotherapy_type == "Adjuvant") %>% 
  select(patientid, chemotherapy_type, cycle_increment, mean_RDI_per_cycledrug) %>% 
  unite(patientid, c(patientid:chemotherapy_type)) %>%
      pivot_wider(names_from = cycle_increment, values_from = mean_RDI_per_cycledrug) %>%
      select(-patientid)

icc_value <- ICC(ICC_df)$results[4, 2]
lb_value <- ICC(ICC_df)$results[4, 7]
up_value <- ICC(ICC_df)$results[4, 8]
```
The ICC value in Upfront Chemo Adj setting is equal to `r icc_value` which means that `r paste("the reliability is", ifelse(icc_value < 0.5, "poor", ifelse( icc_value <0.75, "moderate",ifelse(icc_value<0.9, "good", "excelent"))))`.  
Lower bound and higher bound are `r lb_value` - `r up_value` respectively.

### Upfront Surgery
```{r}
ICC_df <- Treatment_ICC %>% 
  filter(therapy == "Upfront Surgery") %>% 
  select(patientid, chemotherapy_type, cycle_increment, mean_RDI_per_cycledrug) %>% 
  unite(patientid, c(patientid:chemotherapy_type)) %>%
      pivot_wider(names_from = cycle_increment, values_from = mean_RDI_per_cycledrug) %>%
      select(-patientid)

icc_value <- ICC(ICC_df)$results[4, 2]
lb_value <- ICC(ICC_df)$results[4, 7]
up_value <- ICC(ICC_df)$results[4, 8]
```
The ICC value in Upfront Surgery setting is equal to `r icc_value` which means that `r paste("the reliability is", ifelse(icc_value < 0.5, "poor", ifelse( icc_value <0.75, "moderate",ifelse(icc_value<0.9, "good", "excelent"))))`.  
Lower bound and higher bound are `r lb_value` - `r up_value` respectively.

```{r exploratory data analysis}
full_data_study_pop <-
  Treatment %>%
  filter(str_detect(patientid, paste(Frontline$patientid, collapse = "|"))) %>%
  arrange(patientid, episodedate, drugname) %>% 
  filter(had_carbo == "Yes") %>% 
  filter(linenumber_adj == 1)

@@

## <span style="color:green">**Table S0 Summary of the expected, actual dose, and RDI, Crcl, ...**</span>
Here we calculated the mean of amount, CrCl, BSA, height, weight, creatinine,
         target_auc, expected_dose, dose received, 
         RDI per patient/therapy/settings for each drug name.  
The tables show the median IQR for carboplatin calculated over patients with the same therapy (Upfront C or S) and setting (Neo or Adj).
```{r Summary of the expected, actual dose, and RDI}
tbl <- full_data_study_pop %>% 
  # Treatment %>% 
  # # Limit to the patietns after exclusion criteria
  # filter(str_detect(patientid, paste(Frontline$patientid, collapse = "|"))) %>% 
  # arrange(patientid, episodedate, drugname) %>% 
  # # group to have RDI by cycle for each drug 
  # # group_by(patientid, chemotherapy_type, cycle_increment, drugname) %>%
  # # mutate(mean_RDI_per_cycledrug = round(mean(relative_dose_intensity, na.rm = TRUE), 3)
  # # ) %>% 
  # # ungroup() %>% 
  # filter(drugname == "carboplatin") %>% 
  # filter(linenumber_adj == 1) %>%

  group_by(patientid, therapy, chemotherapy_type, drugname) %>% 
  summarise(amount = mean(amount, na.rm = TRUE), 
            BSA = mean(BSA), 
            height = mean(height), 
            weight = mean(weight), 
            creatinine = mean(creatinine),
            CrCl = mean(CrCl),
            target_auc = mean(target_auc),
            expected_dose = mean(expected_dose),
            relative_dose_intensity = mean(mean_RDI_per_drug)) %>% 
  ungroup() %>% 
  mutate(chemotherapy_type = factor(chemotherapy_type, levels = c("Neoadjuvant", "Adjuvant")))

@@

<!-- ## 2.Treatment Plots -->

```{r treatment plots}
full_data_study_pop %>% 
  filter(chemotherapy_type == "Neoadjuvant") %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linename) %>% 
  tbl_summary(label = list(linename ~ "line name received as Neoadujant"))
full_data_study_pop %>% 
  filter(chemotherapy_type == "Adjuvant" & linenumber_adj == 1) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linename, therapy) %>% 
  tbl_summary(by = therapy,
              label = list(linename ~ "line name received as Adjuvant"))
```

```{r}
# full_data_study_pop %>% 
#   filter(chemotherapy_type == "Neoadjuvant") %>% 
#   group_by(patientid, drugname) %>% 
#   summarise(CrCl = mean(CrCl),
#             target_auc = mean(target_auc),
#             expected_dose = mean(expected_dose)) %>% 
#   ungroup() %>% 
#   distinct(patientid, drugname, .keep_all = TRUE) %>% 
#   select(CrCl, target_auc, expected_dose, drugname) %>% 
#   tbl_summary(by = drugname,
#               label = list(CrCl ~ "Average CrCl during Neoadujant setting",
#                            target_auc ~ "Target dose (AUC or mg/mg2)",
#                            expected_dose ~ "Expected dose")
#     )
```

@@

## 1.Plots RDI
## <span style="color:green">**Figure 1: Ridge**</span>  
```{r ggridges, fig.width=16, fig.height=18}
library(ggridges)
# Frontline %>% 
#   pivot_longer(cols = c(RDI_carbo_neo, RDI_pacli_neo, RDI_carbo_adj, RDI_pacli_adj)) %>% 
#   filter(!is.na(value)) %>% 
#   ggplot(aes(y=raceeth, x=value,  fill=raceeth
#              )) +
#     geom_density_ridges(alpha=0.5) +
#     theme_ridges()+
#   theme(#text = element_text(size = 14),#axis.text.y = element_blank(),
#         panel.spacing = unit(0.1, "lines"),
#         strip.text.x = element_text(size = 14)
#     ) +
#   geom_vline(xintercept = 1, color = "red", linetype = 2)+
#   geom_vline(xintercept = 0.85, color = "blue", linetype = 2)+
# 
#   facet_wrap(therapy ~ name, ncol = 2, scales = "free_x")

@@

## <span style="color:green">**Table 2: Summary RDI data by race and bmi**</span>  
Platin  
```{r Table 7 Summary RDI data by race and bmi}
tbl1 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
  select(c(raceeth, "RDI" = RDI_carbo_neo, "RDI cat" = RDI_carbo_neo_grp)) %>%
  tbl_summary(by = raceeth) %>%
  bold_labels() %>% 
  add_p() %>% bold_p(t= 0.05) %>% add_overall()
tbl2 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
  select(c(bmi_cat, "RDI" = RDI_carbo_neo, "RDI cat" = RDI_carbo_neo_grp)) %>%
  tbl_summary(by = bmi_cat) %>%
  bold_labels() %>% 
  add_p() %>% bold_p(t= 0.05) %>% add_overall()

tbl3 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
  select(c(raceeth, "RDI" = RDI_carbo_adj, "RDI cat" = RDI_carbo_adj_grp)) %>%
  tbl_summary(by = raceeth) %>%
  bold_labels() %>% 
  add_p() %>% bold_p(t= 0.05) %>% add_overall()
tbl4 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
  select(c(bmi_cat, "RDI" = RDI_carbo_adj, "RDI cat" = RDI_carbo_adj_grp)) %>%
  tbl_summary(by = bmi_cat) %>%
  bold_labels() %>% 
  add_p() %>% bold_p(t= 0.05) %>% add_overall()

@@

tbl5 <- Frontline %>% filter(therapy == "Upfront Surgery") %>%
  select(c(raceeth, "RDI" = RDI_carbo_adj, "RDI cat" = RDI_carbo_adj_grp)) %>%
  tbl_summary(by = raceeth) %>%
  bold_labels() %>% 
  add_p() %>% bold_p(t= 0.05) %>% add_overall()
tbl6 <- Frontline %>% filter(therapy == "Upfront Surgery") %>%
  select(c(bmi_cat, "RDI" = RDI_carbo_adj, "RDI cat" = RDI_carbo_adj_grp)) %>%
  tbl_summary(by = bmi_cat) %>%
  bold_labels() %>% 
  add_p() %>% bold_p(t= 0.05) %>% add_overall()
